---
title: "p8105_hw6_kl3181"
author: "Kelley Lou"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

```{r load_libraries}
library(tidyverse)
library(modelr)
library(p8105.datasets)
```

### Problem 1

```{r, message = FALSE}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```

Start with one city.

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")
glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```

Try this across cities.

```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI")) 
```

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```



## Problem 2

### Read in datset and tidy. 

```{r, message = FALSE}
baby_df = 
  read_csv("./data/birthweight.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    babysex = as.factor(babysex), 
    mrace = as.factor(mrace),
    malform = as.factor(malform),
    frace = as.factor(frace))
```

Checking NAs
```{r}
count_na = 
  baby_df %>% 
  map_df(~sum(is.na(.)))
```
There are no NAs in the dataframe.

### Build regression model to predict birthweight.

To build my model, I will first create a full model, then remove insignificant variables using a backward step-wise elimination.

```{r, message = FALSE}
# First fitting a model with all variables in the dataset
full_model = lm(bwt ~ ., data = baby_df)

step(full_model, direction = "backward")

# The output provides the following model to have the smallest AIC
model_1 = lm(bwt ~ babysex + bhead + blength + delwt + fincome + 
    gaweeks + mheight + mrace + parity + ppwt + smoken, data = baby_df)

model_1 %>% 
  broom::tidy() %>% 
  select(-std.error, -statistic) %>% 
  knitr::kable()
```

Plotting residuals against fitted values

```{r}
baby_df %>% 
  add_residuals(model_1) %>% 
  add_predictions(model_1) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point(alpha = 0.5) +
  labs(
    title = "Predictions vs. Residuals",
    x = "Prediction",
    y = "Residual"
  )
```

Looking at the distribution of residuals against fitted values, we can see that the most residuals are around 0, and around a predicted value of 3000. There are no clear patterns, but there are a few points that may be outliers. 

### Compare model to other models

Creating model 2 and model 3

```{r}
model_2 = lm(bwt ~ blength + gaweeks, data = baby_df)

model_3 = lm(bwt ~ bhead * blength * babysex, data = baby_df)
```

Cross-validation of models

```{r}
# Map model across each sample 
cv_df = 
  crossv_mc(baby_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )

cv_df = 
  cv_df %>% 
  mutate(
    model_1 = map(.x = train, ~lm(bwt ~ babysex + bhead + blength + delwt + fincome + 
    gaweeks + mheight + mrace + parity + ppwt + smoken, data = .x)),
    model_2 = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    model_3 = map(.x = train, ~lm(bwt ~ bhead * blength * babysex, data = .x))
  ) %>% 
  mutate(
    rmse_model_1 = map2_dbl(model_1, test, ~rmse(model = .x, data = .y)),
    rmse_model_2 = map2_dbl(model_2, test, ~rmse(model = .x, data = .y)),
    rmse_model_3 = map2_dbl(model_3, test, ~rmse(model = .x, data = .y))
    )
```

Check RMSEs to find the best model. 

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_violin(aes(fill = model)) + 
  labs(
    title = "Comparing Models",
    x = "Model",
    y = "rmse"
  )
```

Looking at the models, we can see that model 1 has the lowest RMSE, indicating that it is the best model out of the three.


## Problem 3

Import data.

```{r, message = FALSE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

### Use 5000 bootstrap samples and, for each bootstrap sample, produce estimates of r̂2 and log(β̂ 0∗β1)

```{r, warning = FALSE}
bootstrap_results = 
  weather_df %>% 
  modelr::bootstrap(n = 5000, id = "strap_number") %>% 
  mutate(
    models = map(.x = strap, ~ lm(tmax ~ tmin, data = .x)),
    r_squared = map(models, broom::glance),
    results = map(models, broom::tidy)
  ) %>% 
  unnest(results, r_squared) %>% 
  select(strap_number, term, estimate, r.squared)
```

Wrangling to calculate log(beta0*beta1)

```{r}
beta = 
  bootstrap_results %>% 
  select(strap_number, term, estimate) %>% 
  pivot_wider(
    names_from = term,
    values_from = estimate
  ) %>% 
  janitor::clean_names() %>% 
  mutate(log_beta = log(intercept*tmin))

full_results = left_join(bootstrap_results, beta, by = "strap_number") %>% 
  select(-intercept, -tmin)
```

### Look at distribution of  r̂2 and log(beta0*beta1).

```{r}
full_results %>% 
  ggplot(aes(x = r.squared)) +
  geom_density(fill = "red") +
  labs(
    title = "Distribution of r^2",
    x = "r^2 value"
  )

full_results %>%
  ggplot(aes(x = log_beta)) +
  geom_density(fill = "blue") +
  labs(
    title = "Distribution of log(beta0*beta1)",
    x = "log(beta0*beta1)"
  )
```

The distribution of r squared is mostly normally distributed, centered round 0.91, with a slight left skew. The distribution of log(beta0*beta1) is very similar, centered around 2.02 without clear skewness.

### Finding 95% CI.

```{r, message = FALSE}
full_results %>%
  pivot_longer(
    r.squared:log_beta,
    names_to = "parameter",
    values_to = "value") %>% 
  group_by(parameter) %>% 
  summarize(
    ci_lower = quantile(value, 0.025),
    ci_upper = quantile(value, 0.975)
  ) %>% 
  knitr::kable(digits = 3)
```

The 95% CI for log(beta0*beta1) is 1.967 to 2.058.
The 95% CI for r squared is 0.894 to 0.927.
