---
title: "p8105_hw6_kl3181"
author: "Kelley Lou"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

```{r load_libraries}
library(tidyverse)
library(modelr)
library(p8105.datasets)
```

### Problem 1

```{r}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```

Start with one city.

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")
glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```

Try this across cities.

```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI")) 
```

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```



## Problem 2

### Read in datset and tidy. 

```{r}
baby_df = 
  read_csv("./data/birthweight.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    babysex = as.factor(babysex), 
    mrace = as.factor(mrace),
    malform = as.factor(malform),
    frace = as.factor(frace))
```

### Build regression model to predict birthweight.

To build my model, I will first create a full model, then remove insignificant variables using a backward step-wise elimination.

```{r}
# First fitting a model with all variables in the dataset
full_model = lm(bwt ~ ., data = baby_df)

step(full_model, direction = "backward")

# The output provides the following model to have the smallest AIC
model_1 = lm(bwt ~ babysex + bhead + blength + delwt + fincome + 
    gaweeks + mheight + mrace + parity + ppwt + smoken, data = baby_df)

model_1 %>% 
  broom::tidy() %>% 
  select(-std.error, -statistic) %>% 
  knitr::kable()
```

Plotting residuals against fitted values
```{r}
baby_df %>% 
  add_residuals(model_1) %>% 
  add_predictions(model_1) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point(alpha = 0.5) +
  labs(
    title = "Predictions vs. Residuals",
    x = "Prediction",
    y = "Residual"
  )
```
Looking at the distribution of residuals against fitted values, we can see that the most residuals are around 0, and around a predicted value of 3000. There are no clear patterns, but there are a few points that may be outliers. 

### Compare model to other models

Creating model 2 and model 3
```{r}
model_2 = lm(bwt ~ blength + gaweeks, data = baby_df)

model_3 = lm(bwt ~ bhead * blength * babysex, data = baby_df)
```

Cross-validation of models
```{r}
# Map model across each sample 
cv_df = 
  crossv_mc(baby_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )

cv_df = 
  cv_df %>% 
  mutate(
    model_1 = map(.x = train, ~lm(bwt ~ babysex + bhead + blength + delwt + fincome + 
    gaweeks + mheight + mrace + parity + ppwt + smoken, data = .x)),
    model_2 = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    model_3 = map(.x = train, ~lm(bwt ~ bhead * blength * babysex, data = .x))
  ) %>% 
  mutate(
    rmse_model_1 = map2_dbl(model_1, test, ~rmse(model = .x, data = .y)),
    rmse_model_2 = map2_dbl(model_2, test, ~rmse(model = .x, data = .y)),
    rmse_model_3 = map2_dbl(model_3, test, ~rmse(model = .x, data = .y))
    )
```

Check RMSEs to find the best model. 
```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_violin(aes(fill = model)) + 
  labs(
    title = "Comparing Models",
    x = "Model",
    y = "rmse"
  )
```
Looking at the models, we can see that model 1 has the lowest RMSE, indicating that it is the best model out of the three.


## Problem 3

Import data and tidy.
